### 2020-08-25 code/figureSM2.Rmd

mortpl <- ggplot(menmort) + 
    geom_line(aes(yrnum,nsurv/100000),col="#0072B2",data=menmort) +
    geom_line(aes(yrnum,nsurv/100000),col="#D55E00",data=wommort)+
    stat_function(fun=function(x) mccdf(x),col="#009E73")+
    stat_function(fun=function(x) fccdf(x),col="#E69F00")+labs(title="1-cdf(age) for Men and Women (CDC Data vs  model fit)",x="Age (yrs)",y="1-cdf") +
    theme_minimal()

>>>>

mytheme = theme(
#    axis.text.x = element_blank(),
#    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
#    axis.ticks = element_blank(),
#    axis.line = element_blank(),
    strip.text.y.right = element_text(angle = 0),
    strip.background = element_blank(),
    legend.key.height = unit(0.4, "lines"),
    legend.title = element_blank(),
    #legend.position = "none",
    title = element_text(size=10)
  )

mortpl <- ggplot(menmort) + 
    geom_line(aes(yrnum,nsurv/100000, color = "CDC men"),data=menmort) +
    geom_line(aes(yrnum,nsurv/100000, color ="CDC women"),data=wommort) +
    stat_function(fun=function(x) mccdf(x), aes(color = "Model fit men")) +
    stat_function(fun=function(x) fccdf(x), aes(color = "Model fit women")) + 
    labs(title="1-cdf(age) for Men and Women (CDC Data vs model fit)",x="Age (yrs)",y="1-cdf", color = "") +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          title = element_text(size = 10),
          legend.position = c(0.85, 0.9),
          legend.text = element_text(size = 8),
          legend.key.size = unit(0.4,"cm")) +
    scale_color_manual(values = c("CDC men" = "#0072B2", "CDC women" = "#D55E00", 
                                  "Model fit men" = "#009E73", "Model fit women" = "#E69F00"))

### 2020-08-25 code/survival/survfig.Rmd

	dfktis$cancname = as.factor(sapply(dfktis$parname,function(x) tisnames[x]))
	ggplot(dfktis,aes_(quote(value),quote(cancname))) + geom_density_ridges()+ theme_minimal() + scale_fill_brewer(palette="Paired") + xlim(0,22) + labs(x="ktis multiplier",y="Cancer Type",title="Tissue Specific Effects")
}

>>>>

	dfktis$cancname = as.factor(sapply(dfktis$parname,function(x) tisnames[x]))
	ggplot(dfktis,aes_(quote(value),quote(cancname))) + geom_density_ridges()+ theme_minimal() + scale_fill_brewer(palette="Paired") + xlim(0,22) + labs(x=expression(paste("k"["tis"], " multiplier")),y="Cancer Type",title="Tissue Specific Effects")
}
